Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-06-29 article/04_Discussion.Rmd
proofreading

The second important question posed for this paper was, *how cultural distance between regions develops, and how it is related to spatial distance?* While the idea behind the first question was rather technical -- reproducing already available information in a quantitative way -- the second one had a larger scope. The quantitative representation of an archaeological narrative paths the way for a diverse set of methods to be applied and the analysis undertaken here is merely the beginning. Unfortunately, the small sample size makes it very difficult to obtain meaningful, significant results in this context.

@@

2. The data used for this analysis was collected for another purpose and its application in this context requires a problematic shift in data meaning as explained in section \ref{data-meaning-discussion}.

>>>>

The second important question posed for this paper was, *how cultural distance between regions develops, and how it is related to spatial distance?* While the idea behind the first question was rather technical -- reproducing already available information in a quantitative way -- the second one has a larger scope. The quantitative representation of an archaeological narrative paths the way for a diverse set of methods to be applied and the analysis undertaken here is merely the beginning. Unfortunately, the small sample size makes it very difficult to obtain meaningful, significant results in this context.

@@

2. The data used for this analysis was collected for another purpose and their application in this context requires a problematic shift in data meaning as explained in section \ref{data-meaning-discussion}.
